---
title: "CaseStudy2"
author: "William Hinton"
date: "8/10/2019"
output: 
  html_document: 
    keep_md: true
---
# Introduction 
This R markdown document will be providing analysis of Talent Management. This process is to leverage our data analysis by creating a linear model and then use stepwise model to pick the idea model. After StepWise identifies some key attributes. We will drill down into Tableau to conduct a more meanful analysis. 

##Libraries that are needed for this process.
```{r ,INCLUDE=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(data.table)
library(tidyverse)
library(sqldf)
library(caTools)
library(MASS)
library(caret)
library(leaps)
library(QuantPsyc)
library(GGally)
```
## House cleaning activites Read file
 Read in dataset cleanup dataset, identifies is.na and any columns we do not want to use.
```{r echo=TRUE}
a <-read.csv("C:/SMU_MasterProgram/SummerMay052019/DS_6306_DataScience_402/CaseStudy2/CaseStudy2_2_2/TalentManagement.csv", sep =",", header = TRUE)
#a1_education <- data.frame(sqldf("SELECT COUNT(*), education FROM a GROUP BY education"))  # count of education by state


setnames(a, old=c("ï..Age"), new=c("Age"))
attrJobs <- a
str(a)
#set yes/no to 0,1
attrJobs$Adj[attrJobs$Attrition=="Yes"]<-1  

attrJobs$Adj[attrJobs$Attrition=="No"]<-0


# 1. Model1 A - All variables
model <- lm(attrJobs$Adj ~ OverTime + 
              MaritalStatus + 
              JobRole + 
              Gender + 
              EducationField +
              Department + 
              BusinessTravel + 
              YearsWithCurrManager +
              YearsSinceLastPromotion +
              YearsInCurrentRole + 
              YearsAtCompany + 
              WorkLifeBalance + 
              TrainingTimesLastYear +
              TotalWorkingYears + 
              StockOptionLevel + 
              RelationshipSatisfaction + 
              PerformanceRating +
              PercentSalaryHike + 
              NumCompaniesWorked + 
              MonthlyRate + 
              MonthlyIncome + 
              JobSatisfaction +
              JobLevel + 
              JobInvolvement + 
              HourlyRate + 
              EnvironmentSatisfaction + 
              Education + 
              DistanceFromHome +
              DailyRate +
              Age
            , data = attrJobs)
summary(model)

# 2. Model1 A - All significant variables
model1A <- lm(attrJobs$Adj ~ OverTime + 
              MaritalStatus + 
              JobRole + 
              Gender + 
              BusinessTravel + 
              YearsSinceLastPromotion +
              YearsInCurrentRole + 
              YearsAtCompany +               
              WorkLifeBalance + 
              TrainingTimesLastYear +
              RelationshipSatisfaction +               
              NumCompaniesWorked +               
              JobSatisfaction +              
              JobInvolvement + 
              JobSatisfaction +
              JobInvolvement +               
              DistanceFromHome +              
              Age
            , data = attrJobs)
summary(model1A)

#full fit
full_fit<- lm(attrJobs$Adj ~ OverTime + 
              MaritalStatus + 
              JobRole + 
              Gender + 
              EducationField +
              Department + 
              BusinessTravel + 
              YearsWithCurrManager +
              YearsSinceLastPromotion +
              YearsInCurrentRole + 
              YearsAtCompany + 
              WorkLifeBalance + 
              TrainingTimesLastYear +
              TotalWorkingYears + 
              StockOptionLevel + 
              RelationshipSatisfaction + 
              PerformanceRating +
              PercentSalaryHike + 
              NumCompaniesWorked + 
              MonthlyRate + 
              MonthlyIncome + 
              JobSatisfaction +
              JobLevel + 
              JobInvolvement + 
              HourlyRate + 
              EnvironmentSatisfaction + 
              Education + 
              DistanceFromHome +
              DailyRate +
              Age 
           , data = attrJobs )

step(full_fit, direction="both")

stepw <- lm(formula = attrJobs$Adj ~ OverTime + MaritalStatus + JobRole + 
    Gender + EducationField + BusinessTravel + YearsWithCurrManager + 
    YearsSinceLastPromotion + YearsInCurrentRole + YearsAtCompany + 
    WorkLifeBalance + TrainingTimesLastYear + TotalWorkingYears + 
    RelationshipSatisfaction + NumCompaniesWorked + JobSatisfaction + 
    JobInvolvement + EnvironmentSatisfaction + DistanceFromHome + 
    Age, data = attrJobs)

summary(stepw)

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
